\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}

% Set the page layout
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}

\title{\LARGE Task Management System (TMS) \\}
\author{Team Members: \\
Abdullah Junejo (07154), Syed M.Ather Hashmi (07554), \\
Ali Nisar Shah (07136), Shahjahan Sangrasi (07620)}
\date{\today} % This will automatically add today's date

\begin{document}

\maketitle

\section*{Abstract}
An easy-to-use application designed to help students manage their tasks efficiently, both in short-term and long-term scenarios. This implementation aims to surpass conventional task planners with its advanced features, including automated prioritization, personalized time estimation, and integrated notifications.

\section{User Specification}
\begin{enumerate}
    \item Users can enter tasks manually or by voice.
    \item The app estimates the average time for task completion and suggests personalized times for the user.
    \item Automatic task prioritization based on grade weightage, workload, and due dates, with manual adjustment options.
    \item Recommendations on which task to complete next.
    \item Notifications if the user is accessing distracting apps.
    \item User-friendly and easy interaction.
    \item Seamless task entry.
    \item Soft notifications with customizable design and sound.
    \item Extensive customization for notification settings, including granular and general assignment categories.
    \item Progress and status updates for task tracking.
    \item Synchronization between mobile and PC applications.
    \item Central calendar functionality.
    \item Personalization features.
\end{enumerate}

\section{System Specification}
\begin{itemize}
\item \textbf{Platform Compatibility:} The system will be compatible with major mobile operating systems (iOS and Android) and desktop operating systems (Windows, macOS).

\item \textbf{Data Management with Neo4j:} Utilizes Neo4j Graph Database for storing and querying data. This enables efficient handling of complex relationships between tasks, priorities, user preferences, and deadlines.

\item \textbf{Task Estimation System Specifications::} Machine Learning/Graph Database ???

\item \textbf{Security:} Robust security measures for data protection, including user authentication.

\item \textbf{Scalability:} Designed to efficiently handle a growing number of users and tasks without performance degradation.

\end{itemize}
\section{Functional Requirements}

\section{Non-Functional Requirements}
\section{Diagrams}
\section{References}

\end{document}

